Stage-Splitting a Modal Language

### 2014-07-24 paper/semantics.tex
temp commit

To understand the difficulty of staged evaluation, consider the following
example:
\begin{lstlisting}
#2 (next {1+2}, 3+4)
\end{lstlisting}
This is a stage-\bbone\ expression of type $\rmint$; the pair is a stage-\bbone\
expression of type $(\fut\rmint)\times\rmint$. A conventional call-by-value
evaluation strategy demands that we evaluate both components of the pair to
values before we project from the pair. However, at stage \bbone\ we are not
allowed to evaluate under the \verb|next|; on the other hand, \verb|next {1+2}|
is not a value, in the sense that it requires additional computation steps.

>>>>

To understand the difficulty of staged evaluation, consider the following
example:
\begin{lstlisting}
#2 (next {1+2}, 3+4)
\end{lstlisting}
This is a stage-\bbone\ expression of type $\rmint$; the pair inside it is a
stage-\bbone\ expression of type $(\fut\rmint)\times\rmint$. A conventional
call-by-value evaluation strategy demands that we evaluate both components of
the pair to values before we project from the pair. However, at stage \bbone\ we
are not allowed to evaluate under the \verb|next|; on the other hand, 
\verb|next {1+2}| is not a value, in the sense that it requires additional
computation steps.
